A Framework for Modelling Thin Objects: \\ from Meshing to Shell Finite Element Method

### 2010-03-10 MICCAI2010/paper.tex
Last update for MICCAI (added screenshots for results section)
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@90 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\begin{figure}
\centering
\includegraphics[height=4cm]{images/cylinderHighWireframe}
\includegraphics[height=4cm]{images/cylinderLow}
\caption {Illustration of our method on a simple example. The target is the high resolution cylinder mesh (left) and the start point is a very coarse mesh approximating the shape of a cylinder (right).}
\label{fig-cylinder}
\end{figure}
\begin{figure}
\centering
\includegraphics[height=4cm]{images/cylinderResults2}
\caption {(Left) One-sided Hausdorff distance colour map of the coarse mesh rendered with shells. (Right) One-sided Hausdorff distance colour map after only one iteration of our algorithm. We can notice that differences with the target mesh have been subtantially reduced.}
\label{fig-cylinderResults}
\end{figure}

\section{Results}
\label{sec:results}
\subsection{Meshing of anatomical structures (error maps)}

>>>>

\begin{figure}
\centering
\includegraphics[height=4cm]{images/cylinderHighWireframe}
\includegraphics[height=4cm]{images/cylinderLow}
\caption {Illustration of our method on a simple example. The target is the high resolution cylinder mesh (left) and the start point is a very coarse mesh approximating the shape of a cylinder (right).}
\label{fig-cylinder}
\end{figure}
\begin{figure}
\centering
\includegraphics[height=4cm]{images/resultsCylinder}
\caption {(Left) One-sided Hausdorff distance colour map of the coarse mesh rendered with shells. (Right) One-sided Hausdorff distance colour map after only one iteration of our algorithm. We can notice that differences with the target mesh have been subtantially reduced.}
\label{fig-cylinderResults}
\end{figure}

\section{Results}
\label{sec:results}
\subsection{Meshing of anatomical structures}

This approach has been applied to mesh more complex anatomical structures with curved shell elements. In each case the error is expressed as a percentage of the diagonal of the object's bounding box.

\begin{figure}
\centering
\includegraphics[height=4cm]{images/resultsLiver}
\caption {Left: the targeteted high resolution liver mesh (8,000 triangles). Right: the one-sided Hausdorff distance error map after applying only one iteration of our algorithm to the coarse mesh (1,200 shells)}. 
\label{fig-liver}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=4cm]{images/resultsAnevrism}
\caption {Left: the targeteted high resolution anevrism mesh (28,368 triangles). Right: the one-sided Hausdorff distance error map after applying only one iteration of our algorithm to the coarse mesh (1,160 shells)}.
\label{fig-anevrism}
\end{figure}
